\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.85]{geometry}
\usepackage[hidelinks]{hyperref}
\setlength{\hintscolumnwidth}{3cm}

% Personal information
\name{Alejandro}{Gil Rivera}
\title{AI \& Innovation Ecosystem Consultant}
\address{Manizales}{Colombia}
\phone[mobile]{+57 304 4832350}
\email{gil.rivera.a@gmail.com}
\social[linkedin]{alejandrogilrivera}

\begin{document}
\makecvtitle

% ─────────────────────────────────────────────
\section{About}
% ─────────────────────────────────────────────
Consultant and practitioner with 8+ years of experience across startup ecosystems,
international development organizations, and agricultural technology in Latin America.
Combines direct experience as a \textbf{startup founder} (EU-funded, accelerator alumni),
\textbf{operations leader} in technology companies, and \textbf{research project manager}
for IDH and Conservation International — with active practice building AI automation
systems, intelligent agents, and data pipelines for agricultural operations and SMBs.
Member of three of the most traction-generating \textbf{AI communities in Latin America
and the Caribbean}. Unique dual perspective as both a smallholder coffee producer in
Caldas, Colombia and an AI systems builder, offering authentic first-hand insight into
how AI is transforming startups, ecosystem support organizations, and investment
dynamics across ALC.

% ─────────────────────────────────────────────
\section{Experience}
% ─────────────────────────────────────────────

\cventry{Jun 2024--Mar 2025}{Information System Consultant}%
{IDH (The Sustainable Trade Initiative) \& Conservation International -- HYLEA}{Huila, Colombia}{}{%
\begin{itemize}
  \item Design and development of the HYLEA Information System (\href{https://sihylea.com}{sihylea.com}) for the
        Andean-Amazonian Corridor Pact, supporting sustainable coffee and cacao
        value chains across multiple municipalities in Huila.
  \item \textbf{Methodological framework design} and primary data collection with
        producers, local organizations, and ecosystem support actors.
  \item Construction of \textbf{analytical framework}: taxonomies, monitoring indicators,
        and data governance matrices for multi-stakeholder coordination (IDH, Conservation
        International, municipalities, cooperatives).
  \item Delivered user manuals, sustainability plan (v2.0), and bi-weekly follow-up
        documentation aligned with contractual deliverables.
\end{itemize}}

\cventry{Nov 2024--Mar 2025}{Project Leader}%
{IDH (The Sustainable Trade Initiative) -- LATTE Program}{Colombia}{}{%
\begin{itemize}
  \item Leadership in designing \textbf{climate financing mechanisms} for coffee producers
        across Latin America; research on financial products for smallholders implementing
        climate-resilient practices.
  \item Development of \textbf{data-driven decision tools} for assessing climate resilience
        needs and agricultural adaptation strategies at farm level.
\end{itemize}}

\cventry{Jun 2024--Mar 2025}{Data Project Manager}%
{Colcocoa}{Colombia}{}{%
\begin{itemize}
  \item Implementation of \textbf{data capture and traceability systems} for 50+ hectare
        cacao and agroforestry plantation; multi-team coordination for operational efficiency.
\end{itemize}}

\cventry{Mar 2021--Present}{Financial Officer (Co-founder)}%
{Power Compost}{Colombia}{}{%
\begin{itemize}
  \item Co-founder of circular economy \textbf{climate action startup}; secured and managed
        \textbf{\$100K+ USD in EU grants} (Climate KIC, GIZ) for sustainability initiatives.
  \item Participant in \textbf{Catalyst acceleration program} (Tec de Monterrey);
        subscription-based MVP with consistent MRR and 5\% churn rate; diverted
        14,000+ kg organic waste, 500+ community participants.
\end{itemize}}

\cventry{Aug 2019--Feb 2022}{Operations \& Service Manager}%
{Direktio S.A.S (HealthTech)}{Colombia}{}{%
\begin{itemize}
  \item Leadership of remote \textbf{startup team} of up to 7 (developers, data engineers);
        managed technical projects with annual budgets exceeding \$100K USD.
  \item Implemented \textbf{BI dashboards} (QlikView, Qlik Sense), multi-source ETL
        pipelines, and AWS cloud migration achieving 37\% infrastructure cost reduction.
  \item Client relationship management for \textbf{data integration projects} with
        healthcare institutions in Colombia and Dominican Republic.
\end{itemize}}

\cventry{Apr 2022--Nov 2022}{Sustainability Projects Manager}%
{Carryt (Logistics Tech)}{Colombia}{}{%
\begin{itemize}
  \item Implemented \textbf{blockchain-based carbon compensation} program; 60\% increase
        in CO\textsubscript{2} tons compensated; sustainability loyalty program for
        independent drivers.
\end{itemize}}

\cventry{Feb 2022--Jun 2022}{Operations Director}%
{Saving The Amazon}{Colombia}{}{%
\begin{itemize}
  \item Led operational teams using Agile/SCRUM; coordinated planting of 15,000+ trees
        in the Colombian Amazon region.
\end{itemize}}

% ─────────────────────────────────────────────
\section{Projects}
% ─────────────────────────────────────────────

\cventry{Jan 2023--Present}{Project Director \& AI Systems Builder}%
{Bellavista Coffee}{Manizales, Colombia}{}{%
\begin{itemize}
  \item Operational and financial management of family coffee farm ($\sim$15 ha, 1,300
        masl); transition to \textbf{regenerative agriculture} (biochar, biological
        control, zero agrochemicals).
  \item Built end-to-end \textbf{AI automation pipelines} (n8n + Claude API + Notion)
        for farm data management and operational workflows; developed \textbf{AI-powered
        prospecting system} (Apify + n8n + Claude API) for European specialty roaster
        outreach.
  \item First international export: Honey Castillo in German specialty marketplace
        (Garza Coffee, Germany); managed buyer relationships and quality certification.
\end{itemize}}

\cventry{2024--Present}{Active Member}%
{AI Communities in Colombia -- 3 Leading Networks}{}{}{%
\begin{itemize}
  \item Active participant in three of the most traction-generating \textbf{AI communities
        in Latin America and the Caribbean}, including structured training through
        Aztec Lab (Tec de Monterrey).
  \item Roles include solution co-creation, \textbf{AI agent development}
        (Claude API, MCP integrations, n8n), knowledge sharing, and building applied
        AI use cases for agriculture and SMBs.
\end{itemize}}

% ─────────────────────────────────────────────
\section{Education}
% ─────────────────────────────────────────────
\cventry{2013}{MSc in Supply Chain Management}%
{EM Normandie Business School}{Le Havre, France}{}{}
\cventry{2010}{Bachelor in International Business}%
{Lindenwood University}{St. Charles, MO, USA}{}{}
\cventry{2024}{Impact Investment}%
{Universidad de Los Andes}{Bogotá, Colombia}{}{}
\cventry{2019}{Transformational Leadership}%
{Universidad EAFIT}{Medellín, Colombia}{}{}

% ─────────────────────────────────────────────
\section{Skills}
% ─────────────────────────────────────────────
\cventry{Research \& Analysis}%
{\normalfont \textbf{Primary data collection}, methodological framework design,
\textbf{case study development}, impact narratives,
\textbf{data visualization} (Power BI, Google Sheets, Excel/VBA)}{}{}{}{}

\cventry{AI \& Automation}%
{\normalfont Claude API, \textbf{n8n workflows}, MCP Integrations,
\textbf{AI agent development}, Apify, prompt engineering, vibe coding}{}{}{}{}

\cventry{Project Management}%
{\normalfont \textbf{Agile/SCRUM}, Asana, Notion, multi-stakeholder coordination,
budgets +\$100K USD, remote team leadership}{}{}{}{}

\cventry{Ecosystem Networks}%
{\normalfont \textbf{Startup communities}, EU funding programs (Climate KIC, GIZ),
Catalyst/TecMty accelerator, IDH, Conservation International}{}{}{}{}

\cventry{Languages}%
{\normalfont \textbf{Spanish} (native), \textbf{English} (professional),
French (professional), Portuguese (intermediate)}{}{}{}{}

\end{document}
